Compiling refinement types to dependent types

### 2020-07-02 tex/paper.tex
Start writing about the translation function

>>>>

The translation function $[|\ |]$ maps the typing context $\nonterm G$ to some logic.
In the subsequent text we assume the oracle can decide the resulting proposition
(otherwise it might be left as a separate lemma to be filled out by the user in the core language, or rejected altogether).

For the example oracle being an SMT solver and the syntax of terms also including mathematics, $[|\ |]$ might be defined as
\begin{equation}
\begin{aligned}
  & [| \emptyset |] = \top																						\\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] = [| \nonterm G |] \land [| \{x/v\} \nonterm r |]   \\
  & [| \nonterm r_1 \land \nonterm r_2 |] = [| \nonterm r_1 |] \land [| \nonterm r_2 |]							\\
  & \cdots TODO
\end{aligned}
\end{equation}
